\documentclass[a4paper]{article}

\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}

\newcommand{\mail}[1]{\href{mailto:#1}{#1}}
\newcommand{\doi}[1]{\href{https://dx.#1}{#1}}

\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\begin{center}
	\textbf{\large Leonardo Andreta de Castro} \\
	\href{http://leoad.ec}{http://leoad.ec} \\
	Email: \mail{leoadec@leoad.ec}
\end{center}

\section*{Professional Experience}

\begin{itemize}
	\item[] \makebox[2cm]{2018---current}
				\textbf{Postdoctoral Associate} \\
				 \makebox[2cm]{} Duke University
	\item[] \makebox[2cm]{2014}
	 			\textbf{Teaching Internship for Electromagnetism I and II} \\
	       \makebox[2cm]{} University of São Paulo (Brazil)
\end{itemize}

\section*{Education}
\begin{itemize}
	\item[] \makebox[2cm]{2012---2016} \textbf{PhD in Physics}, University of São Paulo (Brazil) \\
			\makebox[2cm]{} Thesis: \textit{“Protection of quantum systems and the measurement postulate”}, \\
			\makebox[2cm]{} supervised by Prof R d J Napolitano
\end{itemize}
\begin{itemize}
	\item[] \makebox[2cm]{2010---2012} \textbf{Master's Degree in Physics}, University of São Paulo (Brazil) \\
			\makebox[2cm]{} Dissertation: \textit{“Quantum error-correction theory during logic gates and finite-time} \\
			\makebox[2cm]{} \textit{syndrome measurements”}, supervised by Prof R d J Napolitano
\end{itemize}
\begin{itemize}
	\item[] \makebox[2cm]{2006---2009} \textbf{Bachelor's Degree in Physics},  University of São Paulo (Brazil) \\
			\makebox[2cm]{} Undergraduate research:
				\textit{“Decoherence in a two-qubit system and error-correction theory”}, \\
			\makebox[2cm]{} supervised by Prof R d J Napolitano
\end{itemize}

\section*{Preprints}
	\begin{itemize}
		\item[1.] M Newman, \textbf{L A Castro}, K R Brown. \textit{Generating fault-tolerant cluster states from crystal structures}. \href{https://arxiv.org/abs/1909.11817}{arXiv:1909.11817}

		\item[2.] S Majumder, \textbf{L A Castro}, K R Brown. \textit{Real-time calibration with spectator qubits}. \href{https://arxiv.org/abs/1907.03864}{arXiv:1907.03864}
	\end{itemize}

\section*{Published Papers}
	\subsubsection*{Weak Measurements}

	\begin{itemize}
		\item[1.] \textbf{L A Castro}, C A Brasil, R d J Napolitano. \textit{Weak values in collision theory}. Annals of Physics \textbf{392}, 272--286 (2018). \doi{doi.org/10.1016/j.aop.2018.03.014}
	\end{itemize}
	\subsubsection*{Quantum Error Correction}
	\begin{itemize}
		\item[2.] \textbf{L A Castro}, R d J Napolitano. \textit{Error correction in short time steps during the application of quantum gates}. Annals of Physics \textbf{367}, 199--211 (2016). \doi{doi.org/10.1016/j.aop.2016.01.014}
	\end{itemize}

	\subsubsection*{Open Systems and Continuous Measurements}
	\begin{itemize}
		\item[3.] C A Brasil, \textbf{L A Castro}, R d J Napolitano. \textit{Efficient finite-time measurements under thermal regimes}. European Physical Journal Plus \textbf{129}, 206 (2014). \doi{doi.org/10.1140/epjp/i2014-14206-0}

		\item[4.] C A Brasil, \textbf{L A Castro}, R d J Napolitano. \textit{How much time does a measurement take?} Foundations of Physics \textbf{43}, 642--655 (2013). \doi{doi.org/10.1007/s10701-013-9707-7}

		\item[5.] C A Brasil, \textbf{L A Castro}, R d J Napolitano. \textit{Protecting a quantum state from environmental noise by an incompatible finite-time measurement}. Physical Review A \textbf{84}, 022112 (2011). \\ \doi{doi.org/10.1103/PhysRevA.84.022112}
	\end{itemize}

	\subsubsection*{Didactic Articles on Foundations of Quantum Mechanics}

	\begin{itemize}
		\item[6.] \textbf{L A Castro}, O P de S\'{a} Neto, C A Brasil. \textit{An introduction to quantum measurements with a historical motivation}. Acta Physica Slovaca \textbf{69}, 1 (2019). \href{http://www.physics.sk/aps/pub.php?y=2019&pub=aps-19-01}{Open access}

		\item[7.] \textbf{L A Castro}, C A Brasil, R d J Napolitano. \textit{Elliptical orbits in the phase-space quantization}. Revista Brasileira de Ensino de Física \textbf{38}, e3318 (2016). \doi{doi.org/10.1590/1806-9126-RBEF-2016-0067}

		\item[8.] C A Brasil, \textbf{L A Castro}. \textit{Understanding the pointer states}. European Journal of Physics \textbf{36}, 065024 (2015). \doi{doi.org/10.1088/0143-0807/36/6/065024} \\
	\end{itemize}


\section*{Participation in Conferences}

\subsubsection*{Talks Presented}
\begin{enumerate}
	\item \textbf{L A Castro}, P H Leung, P S Iyer, K R Brown. \textit{“Characterizing Unwanted Motional Coupling in Mølmer-Sørensen Gates”}. American Physical Society March Meeting (2019), Boston, United States.
\end{enumerate}

\subsubsection*{Posters Presented}
\begin{enumerate}
	\item \textbf{L A Castro}. \textit{Quantum error correction with continuous measurements.} Australian Institute of Physics Summer Meeting (2017), Sydney, Australia.
	\item \textbf{L A Castro}, R d J Napolitano. \textit{Quantum error correction theory during logical gates and finite syndrome measurements.}
	12th International Conference on Squeezed States and Uncertainty Relations -- ICSSUR (2011), Foz do Iguaçu, Brazil.
\end{enumerate}

\end{document}
